Generalized Linear Mixed Models

### 2009-04-02 docs/inla/inla.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@173 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}
\frametitle{Example:bacteria}
<<bacmcmc,fig=false,echo=true>>=
library(glmmBUGS)
bac = glmmBUGS(y ~ trt, effects='ID', family='binomial',data=bacteria, file='modelx.bug')
startingValues = bac$startingValues
source("getInits.R")
library(BRugs)
library(R2WinBUGS)
bacResult = bugs(bac$ragged, getInits, 
	parameters.to.save = names(getInits()),
  model.file="model.bug", n.chain=3, n.iter=100, n.burnin=10, n.thin=2,
                             program="openbugs") 
bacParams = restoreParams(bacResult, bac$ragged)

@
\end{frame}

>>>>

\begin{frame}[fragile]
\frametitle{Example:bacteria}
{\scriptsize
<<bacmcmc,fig=false,echo=true>>=
library(glmmBUGS)
bac = glmmBUGS(y ~ trt, effects='ID', family='bernoulli',data=bacteria, modelFile='modelx.bug')
startingValues = bac$startingValues
source("getInits.R")
library(BRugs)
library(R2WinBUGS)
bacResult = bugs(bac$ragged, getInits, 
	parameters.to.save = names(getInits()),
  model.file="model.bug", n.chain=3, n.iter=100, n.burnin=10, n.thin=2,
                             program="openbugs") 
bacParams = restoreParams(bacResult, bac$ragged)

@
}
\end{frame}
